Master thesis

### 2017-05-30 02-Introduction.Rmd
Intro init

* Introduce why tropical rainforest are such a good study case
* Define biodiversity 
* Define ecosystem functionning
* Define ecosystem services
* Introduce tropical sylviculture
* Define selective logging
* Introduce biodiversity erosion in tropical rainforests ant its impact
* Introduce Loreau partitionning
* Introduce the interest of modelling
* Introduce the idea to look at biodiversity as both a parameter and an output

Tropical rainforests have fascinated ecologists due to their outstanding diversity [@connell_diversity_1978].

Tropical forests are primary ecosystems in terms of biodiversit and carbon storage [@Lewis2004].

High biodiversity from tropical rainforests is the source of many ecosystem functions, which support ecosystem services.

Biodiversity and ecosystem functionning field is emmering [@Loreau2000].

Selective logging is increasing in tropical forests.

Tropical logging accounts for one eight of global timber production [@Blaser2011].

Selective logging represents a major threat to biodiversity [@Gibson2013].

>>>>

Sutainable forest management in the tropics (i.e. managed selective harvesting of timber) has been widely promoted internationnaly to combat tropical deforestation and degradation [@Zimmerman2012]. Currently tropical logging accounts for one eight of global timber production [@Blaser2011] and is still increasing. Most tropical timber production originates from selective logging, the targeted harvesting of timber from commercial species in a single cuttint cycle [@Martin2015].

On the other hand, tropical rainforests have fascinated ecologists due to their outstanding diversity [@connell_diversity_1978]. Effectively tropical forests host over half of the Earth's biodiversity [@Scheffers2012]. High biodiversity from tropical rainforests is the source of many ecosystem functions. Amongst others, tropical forests play a key role in biogeochemical cycles, including carbone storage [@Lewis2004]. **Add insights into carbon storage role of tropical forest.** Ecosystem functions from tropical forests support numerous ecosystem services, such as timber production and climate regulation.

But several authors argue that selective logging represents a major threat to biodiversity [@Carreno-Rocabado2012; @DeAvila2015; @Gibson2013; @Martin2015; @Zimmerman2012], challenging the sustainable definition from current selective logging. We consequently need to assess both short and long term impacts of selective logging on tropical forest ecosystems to implement better syslvicultural practives in order to reach sustainability.

The question of selective logging impact on tropical forest can be directly related to the emerging field of biodiversity and ecosystem functionning [@Loreau2000]. Tropical forest outstanding biodiversity will be both a factor and a result of forest ecosystem response to logging disturbance. And forest ecosystem response to logging disturbance will directly modify ecosystem functionning in both short and long term. Consequently assessing selective logging effect on tropical forest linking biodiversity and ecosystem seems an obvious and promising way [@Loreau2010]. **Paragraph to fully review !**

Negative short term impacts of selective logging have been assessed [@Carreno-Rocabado2012; @DeAvila2015;  but see @Martin2015]. Much less is known about the long term impact [@Osazuwa-Peters2015]. The main reason is the difficulty to conduct long term empirical study [but see @Herault2010], which can be completed by the use of forest simulators [@Huth2004; @Khler2004; @Ruger2008; @Tietjen2006]. Individual-based models of forest dynamics present the perfect framework to develop such joint biodiversity-ecosystem approaches [@Li]. Individual-based models describe forest 'patches' accumulating carbon through time, assessing tree growth within the patch, or releasing carbon through gap opening [@Bugmann2001]. Up to several dozens of different Plant Functional Types (PFTs) are generally defined and models can sometimes be fully spatially explicit **Cite Pacala et al. 1996**. Recently, the forest growth simulator TROLL [@Chave1999], an individual-based and spatially explicit forest model, was developped to introduce recent advances in plant physiological community. TROLL model relates physiological processes to species-specific functional traits [@Li]. Consequently, TROLL model allow to simulate fully a neotropical forest biodiversity to study biodiversity-ecosystem functionning link response to logging disturbance.

**Major question greater diversity (taxonomic and functional) brought a better resilience to disturbance ?**

### 2017-05-30 05-Disturbance.Rmd
Intro init

```{r config, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls()) ; invisible(gc())
library(knitr)
library(parallel)
library(TROLL)
library(RconTroll)
library(ggplot2)
library(ggrepel)
library(cowplot)
library(entropart)
library(plotly)
library(readr)
opts_chunk$set(
  echo = F, message = F, warning = F, fig.height = 8, fig.width = 8,
    cache = T, cache.lazy = F)
```

# Materials and methods

## TROLL simulator

### Abiotic environment

### Photosynthesis

### Autotrpohic respiration

### Carbon uptake

### Tree growth

### Seed dispersion, production and recruitment

### Mortality

## TROLL sensitivity analysis

### Functional traits

### Seed rain

## Disturbance

### Disturbance module

### Design of experiment

@@

### Outputs anlaysis ?

#### Resistance and resilience metrics

#### Biodiversity partitioning

## Selective logging

### Selective logging module

#### Designation

#### Selection

#### Rotten trees

#### Felling

#### Tracks

#### Gap damages

### Design of experiment

### Outputs analysis ?

#### Resistance and resilience metrics

#### Biodiversity partitioning

>>>>

# Disturbance

## Model description

## Design of experiment

@@

## Outputs anlaysis ?

### Resistance and resilience metrics

### Biodiversity partitioning

### 2017-05-30 docs/master-thesis.tex
Intro init

\begin{document}
\maketitle

@@

\begin{itemize}
\tightlist
\item
  Introduce why tropical rainforest are such a good study case
\item
  Define biodiversity
\item
  Define ecosystem functionning
\item
  Define ecosystem services
\item
  Introduce tropical sylviculture
\item
  Define selective logging
\item
  Introduce biodiversity erosion in tropical rainforests ant its impact
\item
  Introduce Loreau partitionning
\item
  Introduce the interest of modelling
\item
  Introduce the idea to look at biodiversity as both a parameter and an
  output
\end{itemize}

Tropical rainforests have fascinated ecologists due to their outstanding
diversity \citep{connell_diversity_1978}.

Tropical forests are primary ecosystems in terms of biodiversit and
carbon storage \citep{Lewis2004}.

High biodiversity from tropical rainforests is the source of many
ecosystem functions, which support ecosystem services.

Biodiversity and ecosystem functionning field is emmering
\citep{Loreau2000}.

Selective logging is increasing in tropical forests.

Tropical logging accounts for one eight of global timber production
\citep{Blaser2011}.

Selective logging represents a major threat to biodiversity
\citep{Gibson2013}.

\section{Materials and methods}\label{materials-and-methods}

\subsection{TROLL simulator}\label{troll-simulator}

\subsubsection{Abiotic environment}\label{abiotic-environment}

\subsubsection{Photosynthesis}\label{photosynthesis}

\subsubsection{Autotrpohic respiration}\label{autotrpohic-respiration}

\subsubsection{Carbon uptake}\label{carbon-uptake}

\subsubsection{Tree growth}\label{tree-growth}

\subsubsection{Seed dispersion, production and
recruitment}\label{seed-dispersion-production-and-recruitment}

\subsubsection{Mortality}\label{mortality}

\subsection{TROLL sensitivity
analysis}\label{troll-sensitivity-analysis}

\subsubsection{Functional traits}\label{functional-traits}

\subsubsection{Seed rain}\label{seed-rain}

\subsection{Disturbance}\label{disturbance}

\subsubsection{Disturbance module}\label{disturbance-module}

\subsubsection{Design of experiment}\label{design-of-experiment}

@@

\subsubsection{Outputs anlaysis ?}\label{outputs-anlaysis}

\paragraph{Resistance and resilience
metrics}\label{resistance-and-resilience-metrics}

\paragraph{Biodiversity partitioning}\label{biodiversity-partitioning}

\subsection{Selective logging}\label{selective-logging}

\subsubsection{Selective logging module}\label{selective-logging-module}

\paragraph{Designation}\label{designation}

\paragraph{Selection}\label{selection}

\paragraph{Rotten trees}\label{rotten-trees}

\paragraph{Felling}\label{felling}

\paragraph{Tracks}\label{tracks}

\paragraph{Gap damages}\label{gap-damages}

\subsubsection{Design of experiment}\label{design-of-experiment-1}

\subsubsection{Outputs analysis ?}\label{outputs-analysis}

\paragraph{Resistance and resilience
metrics}\label{resistance-and-resilience-metrics-1}

\paragraph{Biodiversity partitioning}\label{biodiversity-partitioning-1}

@@

\bibliography{bibliography/library.bib}

>>>>

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\begin{document}
\maketitle

@@

Sutainable forest management in the tropics (i.e.~managed selective
harvesting of timber) has been widely promoted internationnaly to combat
tropical deforestation and degradation \citep{Zimmerman2012}. Currently
tropical logging accounts for one eight of global timber production
\citep{Blaser2011} and is still increasing. Most tropical timber
production originates from selective logging, the targeted harvesting of
timber from commercial species in a single cuttint cycle
\citep{Martin2015}.

On the other hand, tropical rainforests have fascinated ecologists due
to their outstanding diversity \citep{connell_diversity_1978}.
Effectively tropical forests host over half of the Earth's biodiversity
\citep{Scheffers2012}. High biodiversity from tropical rainforests is
the source of many ecosystem functions. Amongst others, tropical forests
play a key role in biogeochemical cycles, including carbone storage
\citep{Lewis2004}. \textbf{Add insights into carbon storage role of
tropical forest.} Ecosystem functions from tropical forests support
numerous ecosystem services, such as timber production and climate
regulation.

But several authors argue that selective logging represents a major
threat to biodiversity
\citep{Carreno-Rocabado2012, DeAvila2015, Gibson2013, Martin2015, Zimmerman2012},
challenging the sustainable definition from current selective logging.
We consequently need to assess both short and long term impacts of
selective logging on tropical forest ecosystems to implement better
syslvicultural practives in order to reach sustainability.

The question of selective logging impact on tropical forest can be
directly related to the emerging field of biodiversity and ecosystem
functionning \citep{Loreau2000}. Tropical forest outstanding
biodiversity will be both a factor and a result of forest ecosystem
response to logging disturbance. And forest ecosystem response to
logging disturbance will directly modify ecosystem functionning in both
short and long term. Consequently assessing selective logging effect on
tropical forest linking biodiversity and ecosystem seems an obvious and
promising way \citep{Loreau2010}. \textbf{Paragraph to fully review !}

Negative short term impacts of selective logging have been assessed
\citetext{\citealp{Carreno-Rocabado2012}; \citealp{DeAvila2015}; \citealp[but
see][]{Martin2015}}. Much less is known about the long term impact
\citep{Osazuwa-Peters2015}. The main reason is the difficulty to conduct
long term empirical study \citep[but see][]{Herault2010}, which can be
completed by the use of forest simulators
\citep{Huth2004, Khler2004, Ruger2008, Tietjen2006}. Individual-based
models of forest dynamics present the perfect framework to develop such
joint biodiversity-ecosystem approaches \citep{Li}. Individual-based
models describe forest `patches' accumulating carbon through time,
assessing tree growth within the patch, or releasing carbon through gap
opening \citep{Bugmann2001}. Up to several dozens of different Plant
Functional Types (PFTs) are generally defined and models can sometimes
be fully spatially explicit \textbf{Cite Pacala et al. 1996}. Recently,
the forest growth simulator TROLL \citep{Chave1999}, an individual-based
and spatially explicit forest model, was developped to introduce recent
advances in plant physiological community. TROLL model relates
physiological processes to species-specific functional traits
\citep{Li}. Consequently, TROLL model allow to simulate fully a
neotropical forest biodiversity to study biodiversity-ecosystem
functionning link response to logging disturbance.

\textbf{Major question greater diversity (taxonomic and functional)
brought a better resilience to disturbance ?}

\section{Model description}\label{model-description}

\subsection{Overview}\label{overview}

\subsection{Abiotic environment}\label{abiotic-environment}

\subsection{Photosynthesis}\label{photosynthesis}

\subsection{Autotrpohic respiration}\label{autotrpohic-respiration}

\subsection{Carbon uptake}\label{carbon-uptake}

\subsection{Tree growth}\label{tree-growth}

\subsection{Seed dispersion, production and
recruitment}\label{seed-dispersion-production-and-recruitment}

\subsection{Mortality}\label{mortality}

\section{Sensitivity analysis}\label{sensitivity-analysis}

\subsection{Functional traits}\label{functional-traits}

\subsection{Seed rain}\label{seed-rain}

\section{Disturbance}\label{disturbance}

\subsection{Model description}\label{model-description-1}

\subsection{Design of experiment}\label{design-of-experiment}

@@

\subsection{Outputs anlaysis ?}\label{outputs-anlaysis}

\subsubsection{Resistance and resilience
metrics}\label{resistance-and-resilience-metrics}

\subsubsection{Biodiversity
partitioning}\label{biodiversity-partitioning}

\section{Selective logging}\label{selective-logging}

\subsection{Model description}\label{model-description-2}

\subsubsection{Designation}\label{designation}

\subsubsection{Selection}\label{selection}

\subsubsection{Rotten trees}\label{rotten-trees}

\subsubsection{Felling}\label{felling}

\subsubsection{Tracks}\label{tracks}

\subsubsection{Gap damages}\label{gap-damages}

\subsection{Design of experiment}\label{design-of-experiment-1}

\subsection{Outputs analysis ?}\label{outputs-analysis}

\subsubsection{Resistance and resilience
metrics}\label{resistance-and-resilience-metrics-1}

\subsubsection{Biodiversity
partitioning}\label{biodiversity-partitioning-1}

@@

\bibliography{/home/sylvain/Documents/Bibliography/library.bib}

### 2017-05-30 index.Rmd
DOE plot test
Intro init

--- 
site: "bookdown::bookdown_site"
title: "Master thesis"
author: "Sylvain SCHMITT"
date: "`r Sys.Date()`"
output: bookdown::gitbook
csl: bibliography/mee.csl
bibliography: bibliography/library.bib
link-citations: yes
colorlinks: yes
cover-image: images/main.png
---

>>>>

--- 
site: "bookdown::bookdown_site"
title: "Master thesis"
author: "Sylvain SCHMITT"
date: "`r Sys.Date()`"
output: bookdown::gitbook
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
colorlinks: yes
cover-image: images/main.png
---
